---
title: "clean_data"
author: "Glaydston Veloso"
date: "4/22/2018"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Install dependencies
install.packages("readxl")
install.packages("Hmisc")

# Set the current directory as default
sourceDir <- setwd(".")
setwd(sourceDir)
```

## Loading the files

In this point we loading the file to the variable:

- dataToClean

```{r}
library(readxl)
dataToClean <- read_excel("DataToClean.xlsx", 1)  # read first sheet
head(dataToClean[, 1:5])
```

# Fill down

Fill all the colunm with the initial information:

```{r}
library(tidyr)

cleanedData <- dataToClean %>%
  fill(`Area (use fill down)`)
  
head(cleanedData)
```

# Replace a character with a space

```{r} 
library("Hmisc")
library(data.table) 

replaceData = data.table()
replaceData <- dataToClean[, 3];
replaceData[, "Street"] <- lapply(dataToClean[, 3], function(line) { gsub( "å", " ", line) })
replaceData[, "Street"] <- lapply(replaceData[, "Street"], capitalize)

head(replaceData[, 1:2])

# Set the values on the general table
cleanedData[, 3] <- replaceData[, 2]

```

# Capitalize the titles

Here I'm using the function _capitalize_ from the library **Hmisc** to change the titles of the column 4 from the table with support of the _lapply_ function:

```{r}
library("Hmisc")
library(data.table) 

capitalizeData = data.table()
capitalizeData <- dataToClean[, 4];
capitalizeData[, "Street 2"]<- lapply(dataToClean[, 4], capitalize)

head(capitalizeData[, 1:2])

# Set the values on the general table
cleanedData[, 4] <- capitalizeData[, 2]
```

# Unescape the HTML from colun

I've used the library **xml2** to unescape all the HTML characters and the _apply_ function to indicate the we need to run the function on all rows of the table.

```{r}
library("xml2")
library(data.table) 

unescape_html <- function(str){
  xml2::xml_text(xml2::read_html(paste0("<x>", str, "</x>")))
}

unescapeData = data.table()
unescapeData <- dataToClean[, 5];
unescapeData[, "HTML"] <- apply(dataToClean[, 5], MARGIN = 1, unescape_html)
head(unescapeData[, 1:2])

# Set the values on the general table
cleanedData[, 5] <- unescapeData[, 2]
```

# Write the clean to file

In this point we'll use the write.csv function to export the clean data

```{r}
library(readxl)
write.csv(cleanedData, "cleanedData.csv", row.names=F)
cleanedData <- read.csv("cleanedData.csv", stringsAsFactors=F) 
head(cleanedData)
```